Target Markdown

### 2023-11-22 _targets.Rmd
Update graphs with response diversity

```{targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, readRDS(sim_fw_file)),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
    #filter(abs(Std.Estimate) > 0.1)# %>%
    #  mutate(
    #    Response = var_replacement()[Response],
    #    Predictor = var_replacement()[Predictor]
    #  ) %>%
    }),
  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
  tar_target(sem_eff, {
    readRDS(sim_eff_file)
    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

        term_to_del = "richness : rho : Z +"),

@@

        term_to_del = "richness : rho : Z +"

@@

              env_stoch, rho, Z,

@@

              env_stoch, rho, Z, h,

@@

      rho = c(0, .75, 1),

@@

    to$resp_div <- rho_replacement()[as.character(to$rho)]

@@

  tar_target(pred_sr_rho_int,

@@

      rho = seq(0, 1, length.out = 50),

@@

      slope_richness = map2_dbl(rho, avg_int_strength,

@@

            "rho" = .x,

@@

  tar_target(pred_sr_rho_tlvl,

@@

      slope_richness = map2_dbl(rho, w_avg_tlvl,

@@

  tar_target(pred_sr_rho_ct,

@@

      slope_richness = map2_dbl(rho, ct_alive,

@@

  tar_target(pred_sr_rho,
    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),

@@

      "rho" = 0,

@@

  tar_target(pred_stab_comp_rho,

@@

          names(param) <- c("rho", param_name)

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = default_variable_values_pred
          )
        }
        )
    ) %>%
    select(-fix_effect, -values) %>%
    select(-variable) %>%
    mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(rho, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)
  )
)
```

@@

      filter(rho == 0) %>%

@@

  tar_target(p_cpe_rho,

@@

      ggplot(aes(x = rho, y = log(cpe), group = rho)) +

@@

        x = var_replacement()["rho"],

@@

      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_rho

@@

```{r}
tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      x = predictor,
      y = effect,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(cols = vars(response)) +
  labs(x = "Predictor", y = "Total effect") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

@@

```{r}
library(ggbreak)
cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)
p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      y = predictor,
      x = effect,
      color = response,
      alpha = response,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  scale_colour_manual(values = cols) +
  scale_alpha_manual(values = alpha) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #facet_grid(cols = vars(response)) +
  labs(
    x = "Total standardised effect",
    color = "Stability component",
    alpha = "Stability component"
    ) +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    #legend.justification = "right",
    legend.position = "bottom"
  ) +
  scale_x_break(c(-0.3, -0.6))
p_sem_tot_stab_leg <- plot_grid(
  print(p_sem_tot_stab + theme(legend.position = "none")),
  get_legend(p_sem_tot_stab),
  nrow = 2,
  rel_heights = c(1, .05)
)
ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = print(p_sem_tot_stab_leg),
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * .7,
  units = "mm")
```

@@

```{r}
tar_load(pred_stab_comp_rho)
p_pred_sr_rho <- pred_stab_comp_rho %>%
  filter(response == "stab_com") %>%
  mutate(
    variable = var_replacement()[variable],
    resp_div = 1 - rho
    ) %>%
  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = rho_cat_colors()["Low"],
    mid = "white",
    high = rho_cat_colors()["High"],
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = var_replacement()["resp_div"],
    y = "Food-web structure",
    fill = "Slope community stability - Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, unit = "pt")
  )
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 120,
  height = 120 * .45,
  units = "mm")
```

```{r}
tar_load(pred_data)
p_pred_sr_rho_int_env <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 2.0
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(rho),
      fill = as.factor(rho),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = .8) +
  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(
    cols = vars(env_stoch),
    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation", fill = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

@@

```{r}
pred_data_sr_fw <- pred_data %>%
  filter(
    ct_alive %in% c(.1, .3),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    env_stoch == .1,
    w_avg_tlvl %in% c(2.0, 3.0)
    ) %>%
mutate(
  group_ct_alive = case_when(
    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_avg_int_strength = case_when(
    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_w_avg_tlvl = case_when(
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    )) %>%
pivot_longer(starts_with("group_")) %>%
filter(!is.na(value)) %>%
mutate(name = str_remove(name, "group_"))
p_pred_data_sr_fw <- pred_data_sr_fw %>%
  mutate(name = var_replacement()[name]) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = resp_div,
      fill = resp_div,
      linetype = value,
      #alpha = as.factor(avg_int_strength)
      )) +
  geom_line(linewidth = .8) +
  geom_ribbon(
    aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se),
    alpha = .3, color = NA) +
  scale_color_manual(values = rho_cat_colors()) +
  scale_fill_manual(values = rho_cat_colors()) +
  facet_grid(cols = vars(name)) +
  labs(
    x = var_replacement()["richness"],
    y = var_replacement()["stab_com"],
    fill = var_replacement()["resp_div"],
    color = var_replacement()["resp_div"],
    linetype = "Food-web structure value"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  guides(
    linetype = guide_legend(keywidth = 2,
      override.aes = list(fill = NA, alpha = 1)
      ),
    fill = guide_legend(override.aes = list(linetype = 0, alpha = 1))
  )

@@

```{r}
p_pred_sr <- plot_grid(
  p_pred_data_sr_fw + theme(legend.position = "right"),
  p_pred_sr_rho,
  nrow = 2,
  rel_heights = c(.7, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .7,
  units = "mm")
```

>>>>

```{targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, {
    x <- readRDS(sim_fw_file)
    x %>%
      mutate(resp_div = 1 - rho)
  }),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + resp_div, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
    #filter(abs(Std.Estimate) > 0.1)# %>%
    #  mutate(
    #    Response = var_replacement()[Response],
    #    Predictor = var_replacement()[Predictor]
    #  ) %>%
    }),
  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
  tar_target(sem_eff, {
    readRDS(sim_eff_file)
    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

        term_to_del = "richness : resp_div : Z +"),

@@

        term_to_del = "richness : resp_div : Z +"

@@

              env_stoch, resp_div, Z,

@@

              env_stoch, resp_div, Z, h,

@@

      resp_div = 1 - c(0, .75, 1),

@@

@@

  tar_target(pred_sr_resp_div_int,

@@

      resp_div = seq(0, 1, length.out = 50),

@@

      slope_richness = map2_dbl(resp_div, avg_int_strength,

@@

            "resp_div" = .x,

@@

  tar_target(pred_sr_resp_div_tlvl,

@@

      slope_richness = map2_dbl(resp_div, w_avg_tlvl,

@@

  tar_target(pred_sr_resp_div_ct,

@@

      slope_richness = map2_dbl(resp_div, ct_alive,

@@

  tar_target(pred_sr_resp_div,
    map_dfr(list(pred_sr_resp_div_int, pred_sr_resp_div_ct, pred_sr_resp_div_tlvl),

@@

      "resp_div" = 0,

@@

  tar_target(pred_stab_comp_resp_div,

@@

          names(param) <- c("resp_div", param_name)

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = default_variable_values_pred
          )
        }
        )
    ) %>%
    select(-fix_effect, -values) %>%
    select(-variable) %>%
    mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(resp_div, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)
  )
)
```

@@

      filter(resp_div == 0) %>%

@@

  tar_target(p_cpe_resp_div,

@@

      ggplot(aes(x = resp_div, y = log(cpe), group = resp_div)) +

@@

        x = var_replacement()["resp_div"],

@@

      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_resp_div

@@

```{r}
tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "direct") %>%
  #filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(predictor %in% c("resp_div")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x]))
```

@@

```{r}
library(RColorBrewer)
library(ggbreak)
#cols <- c("Community stability" = "black",
#  "Asynchrony" = "blue",
#  "Population stability" = "darkgreen"
#)
custom_stab_color <- c(
  "Community stability" = "black", #"#ffffbf"
  "Asynchrony" = "#91bfdb",
  "Population stability" = "#fc8d59"
)
alpha <- c("Community stability" = 1, "Asynchrony" = 1, "Population stability" = 1)

sem_tot_predictor <- c("richness", "avg_int_strength", "w_avg_tlvl",
  "ct_alive", "Z", "h", "resp_div", "env_stoch")
var_replacement()[sem_tot_predictor]
p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(predictor %in% sem_tot_predictor) %>%
  mutate(
    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
    predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor)], .ordered = TRUE)
) %>%
  ggplot(aes(
      y = predictor,
      x = effect,
      color = response,
      alpha = response,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  scale_colour_manual(values = custom_stab_color) +
  scale_alpha_manual(values = alpha) +
#  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #facet_grid(cols = vars(response)) +
  labs(
    x = "Total standardised effects",
    color = "Stability component",
    alpha = "Stability component"
    ) +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    #legend.justification = "right",
    legend.position = "bottom") +
  guides(
    color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
    ) +
  theme(
    legend.title = element_blank(),
    legend.position = c(.005, .995),
    legend.justification = c("left", "top")
  )
p_sem_tot_stab_leg <- plot_grid(
  print(p_sem_tot_stab +
    theme(
      legend.position = "none",
    )
  ),
  get_legend(p_sem_tot_stab),
  nrow = 2,
  rel_heights = c(1, .05)
)
ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = print(
    p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .4,
  units = "mm")
```

@@

```{r}
tar_load(pred_stab_comp_resp_div)
p_pred_sr_resp_div <- pred_stab_comp_resp_div %>%
  filter(response == "stab_com") %>%
  mutate(
    variable = var_replacement()[variable]
    ) %>%
  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = resp_div_cat_colors()["Low"],
    mid = "white",
    high = resp_div_cat_colors()["High"],
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = var_replacement()["resp_div"],
    y = "Food-web structure",
    fill = "Slope community stability - Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, unit = "pt")
  )
ggsave_multiple(
  paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
  plot = p_pred_sr_resp_div,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 120,
  height = 120 * .45,
  units = "mm")
```

```{r}
tar_load(pred_data)
p_pred_sr_resp_div_int_env <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    resp_div %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 2.0
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(resp_div),
      fill = as.factor(resp_div),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = .8) +
  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(
    cols = vars(env_stoch),
    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation", fill = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

@@

```{r}
pred_data_sr_fw <- pred_data %>%
  filter(
    ct_alive %in% c(.1, .3),
    resp_div %in% c(1, .25),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    env_stoch == .1,
    w_avg_tlvl %in% c(2.0, 3.0)
    ) %>%
mutate(
  group_ct_alive = case_when(
    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_avg_int_strength = case_when(
    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_w_avg_tlvl = case_when(
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    )) %>%
pivot_longer(starts_with("group_")) %>%
filter(!is.na(value)) %>%
mutate(
  name = str_remove(name, "group_"),
  resp_div_cat = str_replace_all(resp_div, resp_div_replacement())
)

breaks_log_richness <- log(c(3, 6, 20))
breaks_log_stab_com <- log(c(250, 500, 1000))

p_pred_data_sr_fw <- pred_data_sr_fw %>%
  mutate(
    name = var_replacement()[name]
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = resp_div_cat,
      fill = resp_div_cat,
      linetype = value,
      #alpha = as.factor(avg_int_strength)
      )) +
  geom_line(linewidth = .8) +
  geom_ribbon(
    aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se),
    alpha = .3, color = NA) +
  scale_color_manual(values = resp_div_cat_colors()) +
  scale_fill_manual(values = resp_div_cat_colors()) +
  scale_x_continuous(breaks = breaks_log_richness, label = exp(breaks_log_richness)) +
  scale_y_continuous(breaks = breaks_log_stab_com, label = exp(breaks_log_stab_com)) +
  facet_grid(cols = vars(name)) +
  labs(
    x = var_replacement()["richness"],
    y = var_replacement()["stab_com"],
    fill = var_replacement()["resp_div"],
    color = var_replacement()["resp_div"],
    linetype = "Food-web structure value"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  guides(
    linetype = guide_legend(keywidth = 2,
      override.aes = list(fill = NA, alpha = 1)
      ),
    fill = guide_legend(override.aes = list(linetype = 0, alpha = 1))
  )

@@

```{r}
p_pred_sr <- plot_grid(
  p_pred_data_sr_fw + theme(legend.position = "right"),
  p_pred_sr_resp_div,
  nrow = 2,
  rel_heights = c(.7, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .7,
  units = "mm")
```
